```{r, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE} 
 library(dplyr) 
 library(tidyr) 
 library(knitr) 
 library(here) 

###CHANGE THESE TWO PATHS. ALSO ADD THOSE COLUMNS WE TALKED ABOUT TO LAYERS_EEZ_BASE; FOR USE ITRS REGIONS
layer_meta <- read.csv(here('metadata_documentation/layers_base.csv'), stringsAsFactors = FALSE) 
layer_path <- 'https://github.com/OHI-Science/ohi-global/tree/draft/region/layers' 

```



# Pressures
"The pressure score, p, describes the cumulative impact of ecological and social stressors in a given year and region which tend to depress the goal score in future years. Pressure scores range from 0 to 1, and include both ecological (p_E) and social pressures (p_S), such that:

$$p=γp_E+(1-γ)p_S$$

where γ=0.5 is the relative weight for ecological vs. social pressures categories. We default to equal weighting as little evidence was available to justify or quantify unequal weights between ecological and social pressures categories. It may be that future work can inform unequal weighting terms γ for individual goals.

For each goal, subgoal, or goal element (e.g. specific habitat), we calculated pressures as an impact-weighted cumulative impact for each pressure category $p_{ecol}^{goal}$ and $p_{soc}^{goal}$. Impact weights are based on a goal’s sensitivity $w_(s_i)^{goal}$ to specific stressors s_i ranked as low $(w_(s_i)^{goal}=1)$, medium $(w_(s_i)^{goal}=2)$, high $(w_(s_i)^{goal}=3)$, or no impact $(w_(s_i)^{goal}=NA)$, as determined by peer-reviewed literature and expert judgment (Fig. SM2 shows the matrix of stressors, goals, and weights). The denominator represents the maximum stressor impact weight for that category and goal. If cumulative pressure load for a goal/component combination exceeds the maximum possible stressor intensity, we cap it to 1.0, i.e. the equivalent to an individual stressor at maximum stress and intensity.
$$p_{cat}^{goal}=min(\frac{1}{(w_{cat,max}^{goal}}\sum_{i=1}^N w_{s_i}^{goal} ×s_i, 1)$$" OHIBC

## Ecological Pressure

We included five subcategories of ecological stressors/pressures: water pollution, climate change, habitat destruction, fishing pressure, and species pollution

-- more about this here and equations; unsure if the way BC calculated it is the same --

### Water Pollution

[prs_pathogens](https://github.com/OHI-Northeast/ne-scores/blob/master/region/layers/prs_pathogens.csv) 

```{r, echo=FALSE, results='hide'}
                                  x <- tempfile(fileext = 'Rmd')
                                  on.exit(unlink(x))
                                  download.file("https://raw.githubusercontent.com/OHI-Northeast/ne-scores/master/metadata_documentation/ohi_model/layers_info/prs_pathogens.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

[prs_sqi](https://github.com/OHI-Northeast/ne-scores/blob/master/region/layers/prs_sqi.csv) 
```{r, echo=FALSE, results='hide'}
                                  x <- tempfile(fileext = 'Rmd')
                                  on.exit(unlink(x))
                                  download.file("https://raw.githubusercontent.com/OHI-Northeast/ne-scores/master/metadata_documentation/ohi_model/layers_info/prs_sqi.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

[prs_trash](https://github.com/OHI-Northeast/ne-scores/blob/master/region/layers/prs_trash.csv) 
```{r, echo=FALSE, results='hide'}
                                  x <- tempfile(fileext = 'Rmd')
                                  on.exit(unlink(x))
                                  download.file("https://raw.githubusercontent.com/OHI-Northeast/ne-scores/master/metadata_documentation/ohi_model/layers_info/prs_trash.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

[prs_wqi](https://github.com/OHI-Northeast/ne-scores/blob/master/region/layers/prs_wqi.csv) 
```{r, echo=FALSE, results='hide'}
                                  x <- tempfile(fileext = 'Rmd')
                                  on.exit(unlink(x))
                                  download.file("https://raw.githubusercontent.com/OHI-Northeast/ne-scores/master/metadata_documentation/ohi_model/layers_info/prs_wqi.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 


### Climate Change

[cc_acid](https://github.com/OHI-Northeast/ne-scores/blob/master/region/layers/cc_acid.csv) 
```{r, echo=FALSE, results='hide'}
                                  x <- tempfile(fileext = 'Rmd')
                                  on.exit(unlink(x))
                                  download.file("https://raw.githubusercontent.com/OHI-Northeast/ne-scores/master/metadata_documentation/ohi_model/layers_info/cc_acid.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

[cc_sst](https://github.com/OHI-Northeast/ne-scores/blob/master/region/layers/cc_sst.csv) 
```{r, echo=FALSE, results='hide'}
                                  x <- tempfile(fileext = 'Rmd')
                                  on.exit(unlink(x))
                                  download.file("https://raw.githubusercontent.com/OHI-Northeast/ne-scores/master/metadata_documentation/ohi_model/layers_info/cc_sst.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

[cc_slr](https://github.com/OHI-Northeast/ne-scores/blob/master/region/layers/cc_slr.csv) 
```{r, echo=FALSE, results='hide'}
                                  x <- tempfile(fileext = 'Rmd')
                                  on.exit(unlink(x))
                                  download.file("https://raw.githubusercontent.com/OHI-Northeast/ne-scores/master/metadata_documentation/ohi_model/layers_info/cc_slr.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

### Fishing
[prs_fishing](https://github.com/OHI-Northeast/ne-scores/blob/master/region/layers/prs_fishing.csv) 
```{r, echo=FALSE, results='hide'}
                                  x <- tempfile(fileext = 'Rmd')
                                  on.exit(unlink(x))
                                  download.file("https://raw.githubusercontent.com/OHI-Northeast/ne-scores/master/metadata_documentation/ohi_model/layers_info/prs_fishing.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

### Habitat Destruction

[hd_intertidal](https://github.com/OHI-Northeast/ne-scores/blob/master/region/layers/hd_intertidal.csv) 
```{r, echo=FALSE, results='hide'}
                                  x <- tempfile(fileext = 'Rmd')
                                  on.exit(unlink(x))
                                  download.file("https://raw.githubusercontent.com/OHI-Northeast/ne-scores/master/metadata_documentation/ohi_model/layers_info/hd_intertidal.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

[hd_subtidal](https://github.com/OHI-Northeast/ne-scores/blob/master/region/layers/hd_subtidal.csv) 
```{r, echo=FALSE, results='hide'}
                                  x <- tempfile(fileext = 'Rmd')
                                  on.exit(unlink(x))
                                  download.file("https://raw.githubusercontent.com/OHI-Northeast/ne-scores/master/metadata_documentation/ohi_model/layers_info/hd_subtidal.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

[prs_hardening](https://github.com/OHI-Northeast/ne-scores/blob/master/region/layers/prs_hardening.csv) 
```{r, echo=FALSE, results='hide'}
                                  x <- tempfile(fileext = 'Rmd')
                                  on.exit(unlink(x))
                                  download.file("https://raw.githubusercontent.com/OHI-Northeast/ne-scores/master/metadata_documentation/ohi_model/layers_info/prs_hardening.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

[prs_aqua_hab](https://github.com/OHI-Northeast/ne-scores/blob/master/region/layers/prs_aqua_hab.csv) 
```{r, echo=FALSE, results='hide'}
                                  x <- tempfile(fileext = 'Rmd')
                                  on.exit(unlink(x))
                                  download.file("https://raw.githubusercontent.com/OHI-Northeast/ne-scores/master/metadata_documentation/ohi_model/layers_info/prs_aqua_hab.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

[prs_sasi](https://github.com/OHI-Northeast/ne-scores/blob/master/region/layers/prs_sasi.csv) 
```{r, echo=FALSE, results='hide'}
                                  x <- tempfile(fileext = 'Rmd')
                                  on.exit(unlink(x))
                                  download.file("https://raw.githubusercontent.com/OHI-Northeast/ne-scores/master/metadata_documentation/ohi_model/layers_info/prs_sasi.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

### Species Pollution

[prs_disease](https://github.com/OHI-Northeast/ne-scores/blob/master/region/layers/prs_disease.csv) 
```{r, echo=FALSE, results='hide'}
                                  x <- tempfile(fileext = 'Rmd')
                                  on.exit(unlink(x))
                                  download.file("https://raw.githubusercontent.com/OHI-Northeast/ne-scores/master/metadata_documentation/ohi_model/layers_info/prs_disease.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

[sp_alien](https://github.com/OHI-Northeast/ne-scores/blob/master/region/layers/sp_alien.csv) 
```{r, echo=FALSE, results='hide'}
                                  x <- tempfile(fileext = 'Rmd')
                                  on.exit(unlink(x))
                                  download.file("https://raw.githubusercontent.com/OHI-Northeast/ne-scores/master/metadata_documentation/ohi_model/layers_info/sp_alien.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

[sp_genetic](https://github.com/OHI-Northeast/ne-scores/blob/master/region/layers/sp_genetic.csv) 
```{r, echo=FALSE, results='hide'}
                                  x <- tempfile(fileext = 'Rmd')
                                  on.exit(unlink(x))
                                  download.file("https://raw.githubusercontent.com/OHI-Northeast/ne-scores/master/metadata_documentation/ohi_model/layers_info/sp_genetic.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

## Social Pressure

[prs_social](https://github.com/OHI-Northeast/ne-scores/blob/master/region/layers/prs_social.csv) 
```{r, echo=FALSE, results='hide'}
                                  x <- tempfile(fileext = 'Rmd')
                                  on.exit(unlink(x))
                                  download.file("https://raw.githubusercontent.com/OHI-Northeast/ne-scores/master/metadata_documentation/ohi_model/layers_info/prs_social.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 


# Resilience 

"Resilience for each goal and region, r, is based on three components: ecological integrity, r_ecol, and regulatory efforts that target specific ecological pressures, r_reg, which combine to address resilience to ecological pressures; and social integrity, r_soc, which addresses social pressures. Each resilience category contains one or more layers reflecting the magnitude of resilience within each region for each year; layers are “activated” to address specific pressures acting on specific goals based on a resilience matrix (Fig. matrix), and active layers are summed to determine a score for each resilience category. Each layer is constrained from 0 to 1.

$$r=γ((\frac{r_{ecol}+r_{reg})}{2})+(1-γ)r_{soc}$$
 

These components are weighted such that resilience to ecological pressures (i.e., ) and resilience to social pressures (i.e., ) reflect the proportional contribution of ecological and social pressures in the pressures model, i.e. $γ=0.5$ (BC OHI)”

## I. Ecological Integrity

“An intact biodiverse ecosystem provides general resilience to ecological pressures by ensuring the system’s ability to maintain functionality in the face of stressors imposed by human activity and climate change. For OHIBC, we consider the area-weighted average conservation status of all species found in the coastal zone (3 nmi offshore) (as resilience to coastal pressures) and found within the entire EEZ (as resilience to pressures not limited to the coast). (BC OHI)”

## II. Regulatory Efforts/Resilience

“Regulatory resilience describes the institutional measures (e.g., rules, regulations, and laws) designed to address ecological pressures. The regulatory resilience datasets are grouped into five categories that address the 5 pressure categories: water pollution, climate change, fishing pressure, habitat destruction and species introductions (invasive species and genetic escapes)(OHI Goals website).” The resilience layers for each category are composed of 3 components: presence of regulations, implementation/enforcement of regulations, and effectiveness/compliance of regulations. We searched for data that would serve as direct measurements or proxy indicators of the extent and successfulness of these components. Federal or state set targets were used as references for calculating resilience scores, and when this information was not available we used choose references we felt reasonable. In cases where multiple data layers are used to calculate one component, they were averaged, and then the three regulatory resilience categories are equally weighted in the overall resilience layer score. (reg metrics table) 

$$regulatory resilience_{layer x} = \frac{presence + implemenation/enforcemnet + effectiveness/compliance}{3}$$

### 1. Water Pollution
[res_water_pollution](https://github.com/OHI-Northeast/ne-scores/blob/master/region/layers/res_water_pollution.csv) 

```{r, echo=FALSE, results='hide'}
                                  x <- tempfile(fileext = 'Rmd')
                                  on.exit(unlink(x))
                                  download.file("https://raw.githubusercontent.com/OHI-Northeast/ne-scores/master/metadata_documentation/ohi_model/layers_info/res_water_pollution.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 


### 2. Climate Change
[res_climate_change](https://github.com/OHI-Northeast/ne-scores/blob/master/region/layers/res_climate_change.csv) 

```{r, echo=FALSE, results='hide'}
                                  x <- tempfile(fileext = 'Rmd')
                                  on.exit(unlink(x))
                                  download.file("https://raw.githubusercontent.com/OHI-Northeast/ne-scores/master/metadata_documentation/ohi_model/layers_info/res_climate_change.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 


### 3. Fishing Pressure
[res_fishing](https://github.com/OHI-Northeast/ne-scores/blob/master/region/layers/res_fishing.csv) 

```{r, echo=FALSE, results='hide'}
                                  x <- tempfile(fileext = 'Rmd')
                                  on.exit(unlink(x))
                                  download.file("https://raw.githubusercontent.com/OHI-Northeast/ne-scores/master/metadata_documentation/ohi_model/layers_info/res_fishing.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 


### 4. Habitat Destruction
[res_hab_destruction](https://github.com/OHI-Northeast/ne-scores/blob/master/region/layers/res_hab_destruction.csv) 

```{r, echo=FALSE, results='hide'}
                                  x <- tempfile(fileext = 'Rmd')
                                  on.exit(unlink(x))
                                  download.file("https://raw.githubusercontent.com/OHI-Northeast/ne-scores/master/metadata_documentation/ohi_model/layers_info/res_hab_destruction.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

### 5. Species Pollution
[res_alien](https://github.com/OHI-Northeast/ne-scores/blob/master/region/layers/res_alien.csv) 

```{r, echo=FALSE, results='hide'}
                                  x <- tempfile(fileext = 'Rmd')
                                  on.exit(unlink(x))
                                  download.file("https://raw.githubusercontent.com/OHI-Northeast/ne-scores/master/metadata_documentation/ohi_model/layers_info/res_alien.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

## III. Social Integrity
[res_social](https://github.com/OHI-Northeast/ne-scores/blob/master/region/layers/res_social.csv) 

“Social resilience describes the social integrity of coastal communities that allow for adaptive responses to social and ecological pressures (BC)” This layer was calculated using data from the US Opportunity Index, Beacon Hill Competitiveness Reports, League of Conservation Voters Scorecards, and the NOAA Office of Science and Technology Social Indicators scores.

$$socialintegrity = \frac{OpportunityIndex + CompetitivenessReport + LCV + SocialIndicators}{4}$$

```{r, echo=FALSE, results='hide'}
                                  x <- tempfile(fileext = 'Rmd')
                                  on.exit(unlink(x))
                                  download.file("https://raw.githubusercontent.com/OHI-Northeast/ne-scores/master/metadata_documentation/ohi_model/layers_info/res_social.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

# Resilience Data Assessment

insert the matrix for quality of data here. use the highlighting functions in kable for the green, yellow, red
