---
title: "Calculate OHI scores"
output: html_document
---

R code to calculate OHI scores with the `ohicore` package.

This is an RMarkdown file, where written text appears with a white background and R code appears with a grey background as a "code chunk". You can run R code line-by-line, or as a whole chunk by clicking the green triangle at the top-right corner of the code chunk's grey box.

----
## Install R packages

Run this code chunk one time only to install packages you don't already have. This is like wiring a building for electricity. *Note: warnings are fine.*

```{r install packages, eval=FALSE}
## install packages from R community
install.packages("tidyverse")
install.packages("zoo")
install.packages("here")
install.packages("devtools")

## install the ohicore package from OHI team
devtools::install_github('ohi-science/ohicore@dev')
```

## Load R packages

Run this every time you calculate scores so that you will have libraries available to you. This is like turning on the lights in a building. Additionally, you will set the working directory to your scenario folder. The syntax `::` identifies which library a function is from.

```{r setup, eval=FALSE}
## load package libraries
library(tidyverse)
library(stringr)
library(zoo)
library(here)
library(ohicore)

#Run following to update the layers.csv file with the latest information in layers_base.csv and to reset 
source("~/github/ne-scores/metadata_documentation/layers_script.R")

## set the working directory to a filepath we all have
setwd(here::here('region'))
options(scipen=999)
```


## Calculate and save scores

Run this chunk to calculate and save scores as `scores` object and as `scores.csv`. You can examine `scores.csv` in the Git tab of RStudio to explore what changed.

```{r calculate scores, eval=FALSE}
## calculate scores for each year scenario and save to a single csv file ----

## select scenario year for the assessment
scenario_years <- c(2005:2017)
scores_all_years <- data.frame()

#because of a weird issue in the ohicore CalculateResilience All function, I created my own resilience function and then 
#force R to use it by sourcing an updated CalculateAll function. Ideally, we fix it in ohicore and remove the next two lines
source("conf/ne_resilience_function.R")
source("conf/ne_pressure_function.R")
source("conf/calculate_all_function.R")

## loop through each scenario year
for (s_year in scenario_years){  # s_year=2017

  message(sprintf('--- Calculating Scores for scenario year %s ----', s_year))

  ## configure checks
  conf   <-  ohicore::Conf('conf')
  ohicore::CheckLayers(layers.csv = 'layers.csv',
            layers.dir = 'layers',
            flds_id    = conf$config$layers_id_fields)
  layers <-  ohicore::Layers(layers.csv = 'layers.csv', layers.dir = 'layers')
  layers$data$scenario_year <-  s_year

  ## calculate scores
  scores_sy <- CalculateAll(conf, layers) %>%
    mutate(year = s_year)

  ## bind scores to dataframe
  scores_all_years <- rbind(scores_all_years, scores_sy)
  
  #add flowerplot code in here so we generate flowerplots for each year. This will need to include s_year in naming

}

#remove region 0 because it's wrong! It takes the average across all regions, INCLUDING the whole Northeast. Region 12 is our new region 0

scores_all_years <- scores_all_years %>%
  filter(region_id > 0) %>%
  mutate(region_id = ifelse(region_id == 12, 0, region_id))

## save .csv file
readr::write_csv(scores_all_years, 'scores.csv', na='')
```

## Create figures

Run this to create flower plots for each region.

```{r plot, eval=FALSE}
## source script (to be incorporated into ohicore)
source('conf/flower_plot.R')

PlotFlower(assessment_name = "US Northeast",
dir_fig_save    = "reports/figures",
year_plot = 2017)
```

Only run this if the above images have changed.
```{r eval=FALSE}
#crop figures because the white space is too big
library(magick) #this library has image_trim
imgs <- list.files("reports/figures", pattern = "^flower_", full.names = T)

for(i in 1:length(imgs)){
  filename <- paste0("reports/figures/trimmed_", basename(imgs[i]))
  img <- image_read(imgs[i])
  img_crop <- image_trim(img)
  image_write(img_crop, filename)
}
```


